Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-06-10 paper/long_version.tex
Auto Update from local Sharelatex

>>>>

\section{Experiments}
Tested this on a Ubuntu 16.04 Linux virtual machine running on Virtual Box with 12 CPUs and 64GB of RAM allocated from the host system.

Running the query shown in the UI screenshot

rows: query time: method: fauxify time:
1k
10k
100k
1000k

Data from notebook performance\_tests.ipynb

\begin{table}
  \caption{Kung Faux Pandas data synthesis method timings}
  \label{included-methods}
  \centering
  \begin{tabular}{p{12em} l p{14em}}
    \toprule
    Method                                 & Source                    & Notes \\
    \midrule
    Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
    DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
    Synthetic dataset Generation Framework & Bindschaedler et al.      & "Plausible Deniability" probabilistic modeling\\
    \bottomrule
  \end{tabular}
\end{table}

Brief explaination of each method.

hmm, that's interesting
